### 2017-03-01 paper/chapters/sigmoid_belief_nets.tex
minor fixed (killed warnings)

Sigmoid Belief Networks (SBN) were described in 1992 by R.M. Neal \cite{neal:1992} representing a specific type of bayesian networks \cite{pearl:1985} shown in Figure \ref{fig:sbn_arch}
In the case of SBNs however, all states are binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modeling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variable in the bayesian framework which means it can be observed, hidden or unknown representing different states of knowledge. As such it can also be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
\end{equation}
where 
\begin{conditions}
  \sigma(x) & $\frac{1}{1 + e^{-x}}$ (sigmoid function)\\
  W_{j,i} & connection weights from state $s_j$ to $s_i$\\
\end{conditions}

To draw samples from this network, it is possible to simply evaluate Equation~\ref{eq:sbn_node} for each visible node.
However prior to that, the SBN first needs to learn how to generate good samples which includes the \emph{learning} and the \emph{inference} problem.\\
Learning means in this context to adjust the weights and biases of the network to be more likely to generate data similar to samples from the given training dataset.
Meanwhile statistical inference is tasked to infer the states of the hidden nodes based on the states in the visible layer.\\

Due to each state being statistically depend on all ancestors, inference means to evaluate all possible configurations of every previous node.
Especially in deep networks, this kind of computation is infeasible as it requires computing exponentially many configurations.\\

>>>>

Sigmoid Belief Networks (SBN) were described in 1992 by R.M. Neal~\cite{neal:1992} representing a specific type of bayesian networks~\cite{pearl:1985} shown in Figure~\ref{fig:sbn_arch}
In the case of SBNs however, all states are binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modeling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variable in the bayesian framework which means it can be observed, hidden or unknown representing different states of knowledge. As such it can also be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
\end{equation}
where 
\begin{conditions}
  \sigma(x) & $\frac{1}{1 + e^{-x}}$ (sigmoid function)\\
  W_{j,i} & connection weights from state $s_j$ to $s_i$\\
\end{conditions}

To draw samples from this network, it is possible to evaluate Equation~\ref{eq:sbn_node} for each visible node.
However prior to that, the SBN first needs to learn how to generate good samples which includes the \emph{learning} and the \emph{inference} problem.\\
Learning means in this context to adjust the weights and biases of the network to be more likely to generate data similar to samples from the given training dataset.
Meanwhile statistical inference is tasked to infer the states of the hidden nodes based on the states in the visible layer.\\

Due to each state being statistically depend on all ancestors, inference means to evaluate all possible configurations of every previous node.
Especially in deep networks, this kind of computation is infeasible as it requires computing exponentially many configurations.
